
---
title: "DataLab Emirhan Igci"
author: "Emirhan Igci"
date: "2025-04-23"
output:
  html_document:
    toc: true       # Inhaltsverzeichnis aktivieren
    #toc_depth: 3    # Maximale Tiefe des Inhaltsverzeichnisses (optional)
    toc_float: true # Inhaltsverzeichnis schwebend anzeigen (optional)
    number_sections: true
    code_folding: hide
---

The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
position the caret at any line or the code chunk, then click "+".

The code chunk appears:
```{r setup, include=FALSE}
if(!require("dplyr")) {install.packages("dplyr"); library("dplyr")}
if(!require("haven")) {install.packages("haven"); library("haven")}
if(!require("tidyr")) {install.packages("tidyr"); library("tidyr")}
if(!require("tibble")) {install.packages("tibble"); library("tibble")}
if(!require("gridExtra")) {install.packages("gridExtra"); library("gridExtra")}
if(!require("grid")) {install.packages("grid"); library("grid")}
if(!require("plotly")) {install.packages("plotly"); library("plotly")}
if(!require("caret")) {install.packages("caret"); library("caret")}
if(!require("factoextra")) {install.packages("factoextra"); library("factoextra")}
if(!require("randomForest")) {install.packages("randomForest"); library("randomForest")}

library(ggplot2)
set.seed(24032003)

knitr::opts_chunk$set(echo = TRUE)
```
``` {r globalFunc, include=FALSE}
summary<-function(x){
  head(x)

}
```
# Einleitung und Zielsetzung



Type any R code in the chunk, for example:
```{r loadData, echo=FALSE}
library(haven)

# Cross Section Nation wide
cross_section_hk <- read_dta("./cross_section/CampusFile_HK_2023.dta")
cross_section_wk <- read_dta("./cross_section/CampusFile_WK_2023.dta")
cross_section_wm <- read_dta("./cross_section/CampusFile_WM_2023.dta")

# Top 12 Cities
panel_hk <- read_dta("./panel/CampusFile_HK_cities.dta")
panel_wk <- read_dta("./panel/CampusFile_WK_cities.dta")
panel_wm <- read_dta("./panel/CampusFile_WM_cities.dta")

```
```{r dataToDF}
cs_hk_df <- data.frame(cross_section_hk)
cs_hk_df <- data.frame(cross_section_hk)
cs_hk_df <- data.frame(cross_section_hk)
```

Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to build and preview an output.
